SMASH companion source code repository

### 2018-11-06 analysis/index.Rmd
wflow_publish("index.Rmd")

---
title: "SMASH companion code resources"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    toc: false
---

@@

@@

[smashr]: https://github.com/stephenslab/smashr
[smash-preprint]: http://arxiv.org/abs/1605.07787
[issues]: https://github.com/stephenslab/smash-paper/issues
[mit-license]: https://opensource.org/licenses/mit-license.html
[zhengrong]: https://github.com/zrxing
[peter]: http://pcarbo.github.io
[matthew]: http://stephenslab.uchicago.edu

>>>>

---
title: "SMASH companion source code repository"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    toc: false
---

@@

## What's included in the git repository

See here for the source repository. This is what you will find in the
repository:

*Fill out this section.*

@@

[smash-github]: https://github.com/stephenslab/smash-paper
[smashr]: https://github.com/stephenslab/smashr
[smash-preprint]: http://arxiv.org/abs/1605.07787
[issues]: https://github.com/stephenslab/smash-paper/issues
[mit-license]: https://opensource.org/licenses/mit-license.html
[zhengrong]: https://github.com/zrxing
[peter]: http://pcarbo.github.io
[matthew]: http://stephenslab.uchicago.edu
